Spatial population structure determines extinction risk in climate-induced range shifts

### 2019-04-14 Manuscript/AmNat_ReSubmission.tex
Updated the data extraction and graphing files to reflect the new analyses in the manuscript and began the revisions in the manuscript itself

Large-scale population movements have been studied for decades in the context of range expansions (e.g. of invasive or reintroduced species), leading to a robust understanding of both the ecological~\citep{hastings2005spatial} and evolutionary~\citep{shine2011evolutionary, excoffier2009genetic} mechanisms shaping such expansions. For example, while the speed of a range expansion can be well approximated by a combination of the species' intrinsic growth rate and dispersal ability~\citep{fisher1937wave, hastings2005spatial}, recent research demonstrates that evolution in both of these traits can increase both the mean and variance of expansion speed through time~\citep{weiss2017rapid, ochocki2017rapid, szHucs2017rapid, shaw2015dispersal, phillips2015evolutionary}. As fundamentally similar spatial processes, it is likely that range shifts will also be subject to the same ecological and evolutionary mechanisms known to drive range expansions. However, range shifts involve several additional complications absent from range expansions, which must be considered when predicting the dynamics of a shifting population. In particular, range shifts begin with far more complex spatial population structure compared to most range expansions. Here and throughout the paper, we use the phrase "spatial population structure" to refer broadly to the spatial distribution of individuals, and their associated genotypes and phenotypes, within a population. Thus, spatial population structure can encompass factors such as spatial clines in trait values and the starkness of abundance declines characterizing the range edge. Range expansions (e.g. of invasive or reintroduced species) typically start from small founding populations brought to a new area and lacking any initial spatial population structure. While such populations form spatial population structure during the expansion process~\citep{weiss2017rapid, ochocki2017rapid}, established populations respond to climate change in the context of preexisting spatial population structure.

Each factor relating to spatial population structure has the potential to affect the dynamics of range shifts under changing climatic conditions. For example, the underlying mechanism causing population declines at the range edge (e.g. declines in carrying capacity versus growth rate) can alter a population's extinction risk during climate driven range shifts~\citep{henry2013eco}. Further, in ranges characterized by a gradient in a trait optimum, the starkness of the range edge can impact the ability of peripheral populations to adapt to the local optimum, with stark range edges leading to better adaptation in peripheral populations~\citep{garcia1997genetic}, though the importance of this for range shifts has not been investigated. Additionally, the nature of dispersal can interact with adaptation to a trait optimum gradient to impact range shift dynamics. When dispersal occurs in a stepping stone manner, maladapted individuals (i.e. individuals whose phenotypes do not match the local optimum) can block the establishment of better adapted genotypes so long as the mismatch is not too severe~\citep{atkins2010local}. While these aspects of spatial population structure have been shown to impact the dynamics of climate-induced range shifts in isolation, it is unclear how and if they might interact.

Further, given the importance of rapid trait evolution in range expansions~\citep{weiss2017rapid, ochocki2017rapid, szHucs2017rapid, shaw2015dispersal, phillips2015evolutionary}, it is necessary to consider the interplay between aspects of spatial population structure and the role of rapid evolution during range shifts. In asexual species, for example, local adaptation to a trait optimum gradient has been shown to interact with dispersal evolution during climate change, driving increased dispersal probability as genotypes shift to keep pace with their environmental optimum~\citep{hargreaves2015fitness}. However, it is unclear how these two processes might interact in a sexually reproducing species in which dispersal and local adaptation are directly linked via gene flow. Under sexual reproduction, evolution of increased dispersal could simultaneously reduce local adaptation to a trait optimum gradient within a population due to increased gene flow throughout the range~\citep{garcia1997genetic, kirkpatrick1997evolution}. In fact, long-distance pollen dispersal in flowering plants has been shown to restrict local adaptation and, when pollen dispersal sufficiently outpaces seed dispersal, to lead to ecological niche shifts, rather than spatial range shifts, in response to simulated climate change~\citep{aguilee2016pollen}. In addition to potential interactions between local adaptation and dispersal evolution, the starkness of the range edge could influence the potential for rapid trait evolution during range shifts by altering the spatial distribution of dispersal phenotypes throughout the range~\citep{henry2013eco, hargreaves2014evolution}, thus altering the diversity of dispersal genotypes present for subsequent evolution during range shifts.

Here, we assess the interaction of two mechanisms responsible for spatial population structure with trait evolution in sexually reproducing populations undergoing range shifts. We develop an individual-based model capable of producing a wide variety of spatial population structures in which males and females are defined by two genetically determined traits, thus allowing for both evolutionary and ecological responses to climate change. One trait determines dispersal ability while the second defines an individual's environmental niche. Using this model, we vary both the severity of the niche optimum gradient and the starkness of the range edge to ascertain how they interact with each other and with the process of trait evolution to impact a population's ability to track a changing climate. Additionally, by contrasting the dynamics of extant and extinct populations, we isolate the factors most strongly contributing to extinction risk during climate change.

@@

\begin{figure}[h!]
\includegraphics[width=1\textwidth]{"/Users/Topher/Desktop/RangeShifts/ShiftingSlopesOther/SchematicFigures/SimExample"}
\caption{A single example of a simulation with a steep niche optimum gradient and a moderately stark range edge. Information on the (a) abundance, (b) dispersal ability, and (c) fitness of individuals in each patch is shown for time periods beginning with the last generation of stable climate conditions ($t = 0$) to $40$ generations after the start of climate change. Log transformed mean dispersal phenotypes (b) are shown for each patch. Average patch fitness (c) was calculated based on the mean niche trait of local individuals and the niche optimum for each patch.}
\label{fig:SimExample}
\end{figure}

@@

\begin{figure}[h!]
\includegraphics[width=1\textwidth]{"/Users/Topher/Desktop/RangeShifts/ShiftingSlopesOther/ResultFigures/MainExtinction"}
\caption{The cumulative probability of extinction due to a moderate speed of climate change in different experimental scenarios. Graphs show the proportion of simulated populations that went extinct through time for scenarios with a (a) flat, (b) shallow, and (c) steep niche optimum gradient, and in ranges characterized by shallow (solid line), moderate (dashed line), or stark (dotted line) edges. In all graphs, a horizontal grey line shows $\%100$ extinction.}
\label{fig:ExtProb}
\end{figure}

@@

\begin{figure}[h!]
\includegraphics[width=1\textwidth]{"/Users/Topher/Desktop/RangeShifts/ShiftingSlopesOther/ResultFigures/DispComposite"}
\caption{Patterns in the evolution and the equilibrium distribution of the dispersal trait, highlighting extant simulations from a moderate speed of climate change. Evolution in dispersal (a and b) is shown as the change in the mean dispersal phenotype of each patch from the beginning of the period of climate change to the end. Positive values indicate an increase in average dispersal ability in the patch. Equilibrium distributions of the dispersal trait (c and d) are shown as log transformed dispersal phenotypes of individuals in populations after $2000$ generations of stable climate conditions. In all panels, values associated with extant populations are shown in dark blue. Results are shown for populations with a flat niche optimum gradient and a gradual range edge (a and c; $n = 155$ extant populations) and for populations with a steep niche optimum gradient and a stark range edge (b and d; $n = 14$ extant populations). Full results for all parameter combinations are provided in Appendix B.}
\label{fig:Disp}
\end{figure}

@@

\begin{figure}[h!]
\includegraphics[width=1\textwidth]{"/Users/Topher/Desktop/RangeShifts/ShiftingSlopesOther/SchematicFigures/f_of_xt"}
\caption{Example visualization of $f(x,t)$ in Cartesian space. The parameters of $f(x,t)$ are shown on the figure at significant points along the $x$ axis. Specifically, $\beta_{t}$ defined the range center, $\gamma$ determined the slope of $f(x,t)$ at the inflection points (i.e. the range edges), and $\tau$ determined the location of the inflection points. The lattice of discrete $\eta$ x $\eta$ patches in which population dynamics occurred is shown beneath. As described in the \textit{Submodels} section of Appendix A, $f(x,t)$ determined the carrying capacity of the patches along the $x$ dimension of the lattice while carrying capacity remained constant within each column along the $y$ dimension. Landscapes were unbounded in the $x$ dimension and implemented with wrapping boundaries in the $y$ dimension.}
\label{Fig:EnvFunction}
\end{figure}

@@

\begin{figure}[h!]
\includegraphics[width=1\textwidth]{"/Users/Topher/Desktop/RangeShifts/ShiftingSlopesOther/SchematicFigures/LifeCycle"}
\caption{The life cycle of simulated populations is shown divided between events contributing to reproduction and dispersal. Each generation began with new offspring dispersing according to their phenotype, after which reproduction occurred in local populations defined by the discrete lattice. After reproduction, all parental individuals perished, resulting in discrete, non-overlapping generations.}
\label{Fig:LifeCycle}
\end{figure}

@@

\begin{figure}[h!]
\includegraphics[width=1\textwidth]{"/Users/Topher/Desktop/RangeShifts/ShiftingSlopesOther/SchematicFigures/Discretization"}
\caption{The carrying capacity of discrete patches along the $x$ dimension of landscapes. From top to bottom, the plots show the carrying capacities for gradual, moderate, and stark range edges. Points represent the carrying capacity of a discrete $\eta$ x $\eta$ patch in the range. The vertical dashed lines indicate the $x$ coordinates at which $f(x,t)$ declines below $0.1$ and the $\gamma$ value for each plot is listed above.}
\label{Fig:LifeCycle}
\end{figure}

@@

\begin{figure}[h!]
\includegraphics[width=1\textwidth]{"/Users/Topher/Desktop/RangeShifts/ShiftingSlopesOther/ResultFigures/SlowExtinction"}
\caption{The cumulative probability of extinction due to a slow speed of climate change in different experimental scenarios. Graphs show the proportion of simulated populations that went extinct through time for scenarios with a (a) flat, (b) shallow, and (c) steep niche optimum gradient, and in ranges characterized by a shallow (solid line), moderate (dashed line), or stark (dotted line) edge. In all graphs, a horizontal grey line shows $\%100$ extinction.}
\label{Fig:ExtProbSlow}
\end{figure}

@@

\begin{figure}[h!]
\includegraphics[width=1\textwidth]{"/Users/Topher/Desktop/RangeShifts/ShiftingSlopesOther/ResultFigures/FastExtinction"}
\caption{The cumulative probability of extinction due to a fast speed of climate change in different experimental scenarios. Graphs show the proportion of simulated populations that went extinct through time for scenarios with a (a) flat, (b) shallow, and (c) steep niche optimum gradient, and in ranges characterized by a shallow (solid line), moderate (dashed line), or stark (dotted line) edge. In all graphs, a horizontal grey line shows $\%100$ extinction.}
\label{Fig:ExtProbFast}
\end{figure}

@@

\begin{figure}[h!]
\includegraphics[width=1\textwidth]{"/Users/Topher/Desktop/RangeShifts/ShiftingSlopesOther/ResultFigures/SlowInitFitSpace"}
\caption{Individual fitness along the $x$ dimension of the landscape at equilibrium. Points represent the mean across simulations and error bars are interquartile ranges. Population status (extinct or successful) was determined for a slow speed of climate change.}
\label{Fig:InitFitSlow}
\end{figure}

\begin{figure}[h!]
\includegraphics[width=1\textwidth]{"/Users/Topher/Desktop/RangeShifts/ShiftingSlopesOther/ResultFigures/MainInitFitSpace"}
\caption{Individual fitness along the $x$ dimension of the landscape at equilibrium. Points represent the mean across simulations and error bars are interquartile ranges. Population status (extinct or successful) was determined for a moderate speed of climate change.}
\label{Fig:InitFit}
\end{figure}

\begin{figure}[h!]
\includegraphics[width=1\textwidth]{"/Users/Topher/Desktop/RangeShifts/ShiftingSlopesOther/ResultFigures/FastInitFitSpace"}
\caption{Individual fitness along the $x$ dimension of the landscape at equilibrium. Points represent the mean across simulations and error bars are interquartile ranges. Population status (extinct or successful) was determined for a fast speed of climate change.}
\label{Fig:InitFitFast}
\end{figure}

\begin{figure}[h!]
\includegraphics[width=1\textwidth]{"/Users/Topher/Desktop/RangeShifts/ShiftingSlopesOther/ResultFigures/SlowDispEvol"}
\caption{Observed dispersal evolution in populations responding to a slow speed of climate change. Positive values indicate an increase in average dispersal ability during climate change. The values associated with populations successfully tracking climate change are shown in dark blue and the total number of surviving populations is indicated in the top left corner. The experimental scenario corresponding to each histogram is indicated on the figure.}
\label{Fig:DispEvolSlow}
\end{figure}

\begin{figure}[h!]
\includegraphics[width=1\textwidth]{"/Users/Topher/Desktop/RangeShifts/ShiftingSlopesOther/ResultFigures/MainDispEvol"}
\caption{Observed dispersal evolution in populations responding to a moderate speed of climate change. Positive values indicate an increase in average dispersal ability during climate change. The values associated with populations successfully tracking climate change are shown in dark blue and the total number of surviving populations is indicated in the top left corner. The experimental scenario corresponding to each histogram is indicated on the figure.}
\label{Fig:DispEvolMain}
\end{figure}

\begin{figure}[h!]
\includegraphics[width=1\textwidth]{"/Users/Topher/Desktop/RangeShifts/ShiftingSlopesOther/ResultFigures/FastDispEvol"}
\caption{Observed dispersal evolution in populations responding to a fast speed of climate change. Positive values indicate an increase in average dispersal ability during climate change. The values associated with populations successfully tracking climate change are shown in dark blue and the total number of surviving populations is indicated in the top left corner. The experimental scenario corresponding to each histogram is indicated on the figure.}
\label{Fig:DispEvolFast}
\end{figure}

\begin{figure}[h!]
\includegraphics[width=1\textwidth]{"/Users/Topher/Desktop/RangeShifts/ShiftingSlopesOther/ResultFigures/SlowInitDispVals"}
\caption{Distributions of the dispersal phenotypes observed in equilibrium populations. Phenotypes associated with populations that ultimately survived climate change are shown in dark blue and the total number of surviving populations is indicated in the top left corner. Vertical dashed lines indicate the dispersal phenotype necessary to produce an expansion wave exactly matching a slow speed of climate change.}
\label{Fig:InitDispSlow}
\end{figure}

\begin{figure}[h!]
\includegraphics[width=1\textwidth]{"/Users/Topher/Desktop/RangeShifts/ShiftingSlopesOther/ResultFigures/MainInitDispVals"}
\caption{Distributions of the dispersal phenotypes observed in equilibrium populations. Phenotypes associated with populations that ultimately survived climate change are shown in dark blue and the total number of surviving populations is indicated in the top left corner. Vertical dashed lines indicate the dispersal phenotype necessary to produce an expansion wave exactly matching a moderate speed of climate change.}
\label{Fig:InitDispMain}
\end{figure}

\begin{figure}[h!]
\includegraphics[width=1\textwidth]{"/Users/Topher/Desktop/RangeShifts/ShiftingSlopesOther/ResultFigures/FastInitDispVals"}
\caption{Distributions of the dispersal phenotypes observed in equilibrium populations. Phenotypes associated with populations that ultimately survived climate change are shown in dark blue and the total number of surviving populations is indicated in the top left corner. Vertical dashed lines indicate the dispersal phenotype necessary to produce an expansion wave exactly matching a fast speed of climate change.}
\label{Fig:InitDispFast}
\end{figure}

>>>>

Large-scale population movements have been studied for decades in the context of range expansions, leading to a robust understanding of both the ecological~\citep{hastings2005spatial} and evolutionary~\citep{shine2011evolutionary, excoffier2009genetic} mechanisms shaping such expansions. For example, while range expansion speed can be well approximated by a combination of the species' intrinsic growth rate and dispersal ability~\citep{fisher1937wave, hastings2005spatial}, recent research demonstrates that evolution in these traits can increase both the mean and variance of expansion speed through time~\citep{szHucs2017rapid, shaw2015dispersal, phillips2015evolutionary}. In particular, laboratory experiments have shown spatial genetic structure to play an important role in the dynamics of range expansions, even over short time periods~\citep{weiss2017rapid,ochocki2017rapid}. While some range expansions (e.g. of invasive or reintroduced species) start from small founding populations lacking any initial spatial structure, others are characterized by far more complex initial spatial population structure (e.g. humans expanding out of Africa or tree expansion following glacial retreat). Climate-driven range shifts fall in the latter category, as populations respond to climate change in the context of preexisting spatial population structure. For example, species' ranges may be characterized by spatial clines in abundance and genetic patterns. Such clines can form in response to a number of extrinsic or intrinsic factors including adaptation to environmental gradients~\citep{kirkpatrick1997evolution}, altered demographic rates throughout the range~\citep{holt2005theoretical}, or interactions with other species~\citep{case2000interspecific}. Importantly for climate-driven range shifts, the factors influencing these spatial patterns will likely shift with the changing climate, causing simultaneous range contraction and expansion at opposite range margins. Thus, climate-driven range shifts will be affected both by the eco-evolutionary dynamics known to impact range expansions and the moving constraints on spatial population structure impacted by changing climatic conditions.

Certain aspects of spatial population structure have the potential to affect the dynamics of range shifts under changing climatic conditions. For example, the underlying mechanism causing population declines at the range edge (e.g. declines in carrying capacity versus growth rate) can alter a population's extinction risk during climate driven range shifts~\citep{henry2013eco}. Further, in ranges characterized by a gradient in a trait optimum, the starkness of the range edge can impact the ability of peripheral populations to adapt to the local optimum, with stark range edges leading to better adaptation in peripheral populations~\citep{garcia1997genetic}, though the importance of this for range shifts has not been investigated. Additionally, the nature of dispersal can interact with adaptation to a trait optimum gradient to impact range shift dynamics. When dispersal occurs in a stepping stone manner, maladapted individuals (i.e. individuals whose phenotypes do not match the local optimum) can block the establishment of better adapted genotypes so long as the mismatch is not too severe~\citep{atkins2010local}. While these aspects of spatial population structure have been shown to impact the dynamics of climate-induced range shifts in isolation, it is unclear how and if they might interact.

Further, given the importance of rapid trait evolution in range expansions~\citep{weiss2017rapid, ochocki2017rapid, szHucs2017rapid, shaw2015dispersal, phillips2015evolutionary}, it is necessary to consider the interplay between aspects of spatial population structure and the role of rapid evolution during range shifts. In asexual species, for example, local adaptation to an environmental gradient has been shown to interact with dispersal evolution during climate change, driving increased dispersal probability as genotypes shift to keep pace with their environmental optimum~\citep{hargreaves2015fitness}. However, it is unclear how these two processes might interact in a sexually reproducing species in which dispersal and local adaptation are directly linked via gene flow. Under sexual reproduction, evolution of increased dispersal could simultaneously reduce adaptation to an environmental gradient due to increased gene flow throughout the range~\citep{garcia1997genetic, kirkpatrick1997evolution}. In fact, long-distance pollen dispersal in flowering plants is predicted to restrict local adaptation and, when pollen dispersal sufficiently outpaces seed dispersal, to lead to ecological niche shifts rather than spatial range shifts in response to climate change~\citep{aguilee2016pollen}. In addition to potential interactions between adaptation and dispersal evolution, the starkness of the range edge could influence the potential for rapid trait evolution during range shifts by altering the spatial distribution of dispersal phenotypes throughout the range~\citep{henry2013eco, hargreaves2014evolution}, thus altering the diversity of dispersal genotypes present for subsequent evolution during range shifts.

Here, we assess the interaction of two mechanisms responsible for spatial population structure (edge type and an environmental gradient in a trait optimum) with trait evolution in sexually reproducing populations undergoing range shifts. We develop an individual-based model capable of producing a wide variety of spatial population structures in which males and females are defined by two genetically determined traits, thus allowing for both evolutionary and ecological responses to climate change. One trait determines dispersal ability while the second defines an individual's environmental niche. Using this model, we vary both the environmental gradient in the niche optimum and the starkness of the range edge to ascertain how they interact with each other and with the process of trait evolution to impact a population's ability to track a changing climate. Previous research suggests evolution of heightened dispersal during the range shift might alleviate the extinction risk of moving populations~\citep{hargreaves2015fitness, boeye2013more, henry2013eco}, but we predict steep environmental gradients and stark range edges may inhibit such evolution and thus increase extinction risk.

@@

\begin{figure}[h!]
\includegraphics[width=1\textwidth]{"/Users/Topher/Desktop/PostdocResearch/ShiftingSlopesOther/SchematicFigures/SimExample"}
\caption{A single example of a simulation with a steep niche optimum gradient and a moderately stark range edge. Information on the (a) abundance, (b) dispersal ability, and (c) fitness of individuals in each patch is shown for time periods beginning with the last generation of stable climate conditions ($t = 0$) to $40$ generations after the start of climate change. Log transformed mean dispersal phenotypes (b) are shown for each patch. Average patch fitness (c) was calculated based on the mean niche trait of local individuals and the niche optimum for each patch.}
\label{fig:SimExample}
\end{figure}

@@

\begin{figure}[h!]
\includegraphics[width=1\textwidth]{"/Users/Topher/Desktop/PostdocResearch/ShiftingSlopesOther/ResultFigures/MainExtinction"}
\caption{The cumulative probability of extinction due to a moderate speed of climate change in different experimental scenarios. Graphs show the proportion of simulated populations that went extinct through time for scenarios with a (a) flat, (b) shallow, and (c) steep niche optimum gradient, and in ranges characterized by shallow (solid line), moderate (dashed line), or stark (dotted line) edges. In all graphs, a horizontal grey line shows $\%100$ extinction.}
\label{fig:ExtProb}
\end{figure}

@@

%\begin{figure}[h!]
%\includegraphics[width=1\textwidth]{"/Users/Topher/Desktop/PostdocResearch/ShiftingSlopesOther/ResultFigures/DispComposite"}
%\caption{Patterns in the evolution and the equilibrium distribution of the dispersal trait, highlighting extant simulations from a moderate speed of climate change. Evolution in dispersal (a and b) is shown as the change in the mean dispersal phenotype of each patch from the beginning of the period of climate change to the end. Positive values indicate an increase in average dispersal ability in the patch. Equilibrium distributions of the dispersal trait (c and d) are shown as log transformed dispersal phenotypes of individuals in populations after $2000$ generations of stable climate conditions. In all panels, values associated with extant populations are shown in dark blue. Results are shown for populations with a flat niche optimum gradient and a gradual range edge (a and c; $n = 155$ extant populations) and for populations with a steep niche optimum gradient and a stark range edge (b and d; $n = 14$ extant populations). Full results for all parameter combinations are provided in Appendix B.}
%\label{fig:Disp}
%\end{figure}

%\clearpage

@@

\begin{figure}[h!]
\includegraphics[width=1\textwidth]{"/Users/Topher/Desktop/PostdocResearch/ShiftingSlopesOther/SchematicFigures/f_of_xt"}
\caption{Example visualization of $f(x,t)$ in Cartesian space. The parameters of $f(x,t)$ are shown on the figure at significant points along the $x$ axis. Specifically, $\beta_{t}$ defined the range center, $\gamma$ determined the slope of $f(x,t)$ at the inflection points (i.e. the range edges), and $\tau$ determined the location of the inflection points. The lattice of discrete $\eta$ x $\eta$ patches in which population dynamics occurred is shown beneath. As described in the \textit{Submodels} section of Appendix A, $f(x,t)$ determined the carrying capacity of the patches along the $x$ dimension of the lattice while carrying capacity remained constant within each column along the $y$ dimension. Landscapes were unbounded in the $x$ dimension and implemented with wrapping boundaries in the $y$ dimension.}
\label{Fig:EnvFunction}
\end{figure}

@@

\begin{figure}[h!]
\includegraphics[width=1\textwidth]{"/Users/Topher/Desktop/PostdocResearch/ShiftingSlopesOther/SchematicFigures/LifeCycle"}
\caption{The life cycle of simulated populations is shown divided between events contributing to reproduction and dispersal. Each generation began with new offspring dispersing according to their phenotype, after which reproduction occurred in local populations defined by the discrete lattice. After reproduction, all parental individuals perished, resulting in discrete, non-overlapping generations.}
\label{Fig:LifeCycle}
\end{figure}

@@

\begin{figure}[h!]
\includegraphics[width=1\textwidth]{"/Users/Topher/Desktop/PostdocResearch/ShiftingSlopesOther/SchematicFigures/Discretization"}
\caption{The carrying capacity of discrete patches along the $x$ dimension of landscapes. From top to bottom, the plots show the carrying capacities for gradual, moderate, and stark range edges. Points represent the carrying capacity of a discrete $\eta$ x $\eta$ patch in the range. The vertical dashed lines indicate the $x$ coordinates at which $f(x,t)$ declines below $0.1$ and the $\gamma$ value for each plot is listed above.}
\label{Fig:LifeCycle}
\end{figure}

@@

\begin{figure}[h!]
\includegraphics[width=1\textwidth]{"/Users/Topher/Desktop/PostdocResearch/ShiftingSlopesOther/ResultFigures/SlowExtinction"}
\caption{The cumulative probability of extinction due to a slow speed of climate change in different experimental scenarios. Graphs show the proportion of simulated populations that went extinct through time for scenarios with a (a) flat, (b) shallow, and (c) steep niche optimum gradient, and in ranges characterized by a shallow (solid line), moderate (dashed line), or stark (dotted line) edge. In all graphs, a horizontal grey line shows $\%100$ extinction.}
\label{Fig:ExtProbSlow}
\end{figure}

@@

\begin{figure}[h!]
\includegraphics[width=1\textwidth]{"/Users/Topher/Desktop/PostdocResearch/ShiftingSlopesOther/ResultFigures/FastExtinction"}
\caption{The cumulative probability of extinction due to a fast speed of climate change in different experimental scenarios. Graphs show the proportion of simulated populations that went extinct through time for scenarios with a (a) flat, (b) shallow, and (c) steep niche optimum gradient, and in ranges characterized by a shallow (solid line), moderate (dashed line), or stark (dotted line) edge. In all graphs, a horizontal grey line shows $\%100$ extinction.}
\label{Fig:ExtProbFast}
\end{figure}

@@

%\begin{figure}[h!]
%\includegraphics[width=1\textwidth]{"/Users/Topher/Desktop/PostdocResearch/ShiftingSlopesOther/ResultFigures/SlowInitFitSpace"}
%\caption{Individual fitness along the $x$ dimension of the landscape at equilibrium. Points represent the mean across simulations and error bars are interquartile ranges. Population status (extinct or successful) was determined for a slow speed of climate change.}
%\label{Fig:InitFitSlow}
%\end{figure}

%\clearpage

%\begin{figure}[h!]
%\includegraphics[width=1\textwidth]{"/Users/Topher/Desktop/PostdocResearch/ShiftingSlopesOther/ResultFigures/MainInitFitSpace"}
%\caption{Individual fitness along the $x$ dimension of the landscape at equilibrium. Points represent the mean across simulations and error bars are interquartile ranges. Population status (extinct or successful) was determined for a moderate speed of climate change.}
%\label{Fig:InitFit}
%\end{figure}

%\clearpage

%\begin{figure}[h!]
%\includegraphics[width=1\textwidth]{"/Users/Topher/Desktop/PostdocResearch/ShiftingSlopesOther/ResultFigures/FastInitFitSpace"}
%\caption{Individual fitness along the $x$ dimension of the landscape at equilibrium. Points represent the mean across simulations and error bars are interquartile ranges. Population status (extinct or successful) was determined for a fast speed of climate change.}
%\label{Fig:InitFitFast}
%\end{figure}

%\clearpage

%\begin{figure}[h!]
%\includegraphics[width=1\textwidth]{"/Users/Topher/Desktop/PostdocResearch/ShiftingSlopesOther/ResultFigures/SlowDispEvol"}
%\caption{Observed dispersal evolution in populations responding to a slow speed of climate change. Positive values indicate an increase in average dispersal ability during climate change. The values associated with populations successfully tracking climate change are shown in dark blue and the total number of surviving populations is indicated in the top left corner. The experimental scenario corresponding to each histogram is indicated on the figure.}
%\label{Fig:DispEvolSlow}
%\end{figure}

%\clearpage

%\begin{figure}[h!]
%\includegraphics[width=1\textwidth]{"/Users/Topher/Desktop/PostdocResearch/ShiftingSlopesOther/ResultFigures/MainDispEvol"}
%\caption{Observed dispersal evolution in populations responding to a moderate speed of climate change. Positive values indicate an increase in average dispersal ability during climate change. The values associated with populations successfully tracking climate change are shown in dark blue and the total number of surviving populations is indicated in the top left corner. The experimental scenario corresponding to each histogram is indicated on the figure.}
%\label{Fig:DispEvolMain}
%\end{figure}

%\clearpage

%\begin{figure}[h!]
%\includegraphics[width=1\textwidth]{"/Users/Topher/Desktop/PostdocResearch/ShiftingSlopesOther/ResultFigures/FastDispEvol"}
%\caption{Observed dispersal evolution in populations responding to a fast speed of climate change. Positive values indicate an increase in average dispersal ability during climate change. The values associated with populations successfully tracking climate change are shown in dark blue and the total number of surviving populations is indicated in the top left corner. The experimental scenario corresponding to each histogram is indicated on the figure.}
%\label{Fig:DispEvolFast}
%\end{figure}

%\clearpage

%\begin{figure}[h!]
%\includegraphics[width=1\textwidth]{"/Users/Topher/Desktop/PostdocResearch/ShiftingSlopesOther/ResultFigures/SlowInitDispVals"}
%\caption{Distributions of the dispersal phenotypes observed in equilibrium populations. Phenotypes associated with populations that ultimately survived climate change are shown in dark blue and the total number of surviving populations is indicated in the top left corner. Vertical dashed lines indicate the dispersal phenotype necessary to produce an expansion wave exactly matching a slow speed of climate change.}
%\label{Fig:InitDispSlow}
%\end{figure}

%\clearpage

%\begin{figure}[h!]
%\includegraphics[width=1\textwidth]{"/Users/Topher/Desktop/PostdocResearch/ShiftingSlopesOther/ResultFigures/MainInitDispVals"}
%\caption{Distributions of the dispersal phenotypes observed in equilibrium populations. Phenotypes associated with populations that ultimately survived climate change are shown in dark blue and the total number of surviving populations is indicated in the top left corner. Vertical dashed lines indicate the dispersal phenotype necessary to produce an expansion wave exactly matching a moderate speed of climate change.}
%\label{Fig:InitDispMain}
%\end{figure}

%\clearpage

%\begin{figure}[h!]
%\includegraphics[width=1\textwidth]{"/Users/Topher/Desktop/PostdocResearch/ShiftingSlopesOther/ResultFigures/FastInitDispVals"}
%\caption{Distributions of the dispersal phenotypes observed in equilibrium populations. Phenotypes associated with populations that ultimately survived climate change are shown in dark blue and the total number of surviving populations is indicated in the top left corner. Vertical dashed lines indicate the dispersal phenotype necessary to produce an expansion wave exactly matching a fast speed of climate change.}
%\label{Fig:InitDispFast}
%\end{figure}
